Inference methods comparison for the simplified Naomi model using maximum mean discrepancy

### 2023-12-31 src/naomi-simple_mmd/mmd.Rmd
Add MMD output for thesis

round(100 * (mmd_aghq@mmdstats[1] - mmd_tmb@mmdstats[1]) / mmd_tmb@mmdstats[1])
round(100 * (mmd_aghq@mmdstats[2] - mmd_tmb@mmdstats[2]) / mmd_tmb@mmdstats[2])
```

>>>>

round(100 * (mmd_aghq@mmdstats[1] - mmd_tmb@mmdstats[1]) / mmd_tmb@mmdstats[1])
round(100 * (mmd_aghq@mmdstats[2] - mmd_tmb@mmdstats[2]) / mmd_tmb@mmdstats[2])

saveRDS(list(mmd_tmb = mmd_tmb, mmd_aghq = mmd_aghq), file = "mmd.rds")
```
